Rule-Based Normalization of German Twitter Messages

### 2013-08-21 darmstadt_gscl_2013/article_twitter_normalization.tex
next to last update before merges from Tatjana

A closer look at unknown words which were classified as misspellings
revealed that a prevailing majority of them was considered as
colloquial spelling variants. Such variants accounted for 70.5~\% of
detected spelling mistakes in \texttt{hunspell} data and for 66.17~\%
of misspellings recognized by \texttt{TreeTagger}. Frequency
distributions of colloquial and non-colloquial misspellings in data
analyzed with either tools are shown in Figures
\ref{fig:misspl-hunspell} and \ref{fig:misspl-ttagger}.
\begin{figure}[ht]
  \centering
  \begin{minipage}[b]{0.45\linewidth}
    \caption{Frequency distributions of non-standard spellings in data
      analyzed with \texttt{hunspell}}
    \includegraphics[width=\textwidth]{data/img/hunspell_spell.png}
    \label{fig:misspl-hunspell}
  \end{minipage}
  \hspace{0.5cm}
  \begin{minipage}[b]{0.45\linewidth}
    \caption{Frequency distributions of non-standard spellings in data
      analyzed with \texttt{TreeTagger}}
    \includegraphics[width=\textwidth]{data/img/treetagger_spell.png}
    \label{fig:misspl-ttagger}
  \end{minipage}
\end{figure}

>>>>

A closer look at unknown words classified as misspellings revealed
that a prevailing majority of them was considered as colloquial
spelling variants. Such variants accounted for 70.5~\% of detected
spelling mistakes in \texttt{hunspell} data and for 66.17~\% of
misspellings recognized by \texttt{TreeTagger}. Frequency
distributions of colloquial and non-colloquial misspellings in data
analyzed with either tools are shown in Figures
\ref{fig:misspl-hunspell} and \ref{fig:misspl-ttagger}.
\begin{figure}[ht]
  \centering
  \begin{minipage}[b]{0.45\linewidth}
    \caption{Frequency distributions of non-standard spellings in data
      analyzed with \texttt{hunspell}}
    \includegraphics[width=\textwidth]{data/img/hunspell_spell.png}
    \label{fig:misspl-hunspell}
  \end{minipage}
  \hspace{0.5cm}
  \begin{minipage}[b]{0.45\linewidth}
    \caption{Frequency distributions of non-standard spellings in data
      analyzed with \texttt{TreeTagger}}
    \includegraphics[width=\textwidth]{data/img/treetagger_spell.png}
    \label{fig:misspl-ttagger}
  \end{minipage}
\end{figure}
